---
title: "R Notebook"
output: rmdformats::readthedown
# output:
#   html_document:
#     df_print: kable
#     keep_md: yes
---
# Pre-processing and visualization
Original code by Kamran Afzali, adapted by Jeanne Racicot



Load packages

```{r echo = T, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(gridExtra)
library(lmerTest)
library(lme4)
library(glmnet)
library(glmmLasso)
library(MASS)
library(nlme)
library(knitr)
library(kableExtra)
scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}
```


Load data from prefrontal atlas


```{r echo = T, message=FALSE}
data <- read_csv("output_data/dataframe_day2day.csv")
conn_names <- read_csv("output_data/105_connection_names_reversed.csv")
```

Tally


```{r}
data %>% group_by(subject) %>% tally()
by_id <- data %>% group_by(subject)
by_id <- by_id %>% 
  mutate(daysFromFirstScan_STD=scale_this(daysFromFirstScan))
data$daysFromFirstScan_STD=by_id$daysFromFirstScan_STD
```


```{r}
plots=list()

subs=unique(data$subject)
i=1
for (s in subs) {
x=as.numeric(data$daysFromFirstScan[data$subject==s])
y1=as.numeric(as.character(data$PANAS_PA[data$subject==s])) 
PosA=rep("PA",length(y1))
y2=as.numeric(as.character(data$PANAS_NA[data$subject==s])) 
NegA=rep("NA",length(y2))

Data=as.data.frame(rbind(cbind(day=x,outcome=PosA,value=as.numeric(as.character(y1))),
cbind(day=x,outcome=NegA,value=as.numeric(as.character(y2)))))  


Data$day=as.numeric(as.character(Data$day))
plots[[i]]=ggplot( Data, aes(x = day, y = value, group=outcome, color=outcome)) +
  geom_line()+geom_point()+ggtitle(as.character(s))
i=i+1
rm(Data)
}
```


## Outcome plots per subject

```{r fig1, fig.height = 10, fig.width = 14, fig.align = "center"}
do.call(grid.arrange,plots)
```

```{r include=FALSE}
head(data)
```

## Data pre-processiong, creating BP and WP variables
Between person is the mean of every connection for every session and subject
Within person is each connection, centered to 0 (value-mean)


```{r}
dataML <-by_id %>% summarise(
  C1BP = mean(connection1),  
  C2BP = mean(connection2), 
  C3BP = mean(connection3), 
  C4BP = mean(connection4), 
  C5BP = mean(connection5), 
  C6BP = mean(connection6), 
  C7BP = mean(connection7), 
  C8BP = mean(connection8), 
  C9BP = mean(connection9), 
  C10BP = mean(connection10), 
  C11BP = mean(connection11), 
  C12BP = mean(connection12), 
  C13BP = mean(connection13),
  C14BP = mean(connection14),
  C15BP = mean(connection15),
  C16BP = mean(connection16),
  C17BP = mean(connection17),
  C18BP = mean(connection18),
  C19BP = mean(connection19),
  C20BP = mean(connection20),
  C21BP = mean(connection21),
  C22BP = mean(connection22),
  C23BP = mean(connection23),
  C24BP = mean(connection24),
  C25BP = mean(connection25),
  C26BP = mean(connection26),
  C27BP = mean(connection27),
  C28BP = mean(connection28),
  C29BP = mean(connection29),
  C30BP = mean(connection30),
  C31BP = mean(connection31),
  C32BP = mean(connection32), 
  C33BP = mean(connection33),
  C34BP = mean(connection34),
  C35BP = mean(connection35),
  C36BP = mean(connection36),
  C37BP = mean(connection37),
  C38BP = mean(connection38),
  C39BP = mean(connection39),
  C40BP = mean(connection40),
  C41BP = mean(connection41),
  C42BP = mean(connection42),
  C43BP = mean(connection43),
  C44BP = mean(connection44),
  C45BP = mean(connection45),
  C46BP = mean(connection46),
  C47BP = mean(connection47),
  C48BP = mean(connection48),
  C49BP = mean(connection49),
  C50BP = mean(connection50),
  C51BP = mean(connection51),
  C52BP = mean(connection52),
  C53BP = mean(connection53),
  C54BP = mean(connection54),
  C55BP = mean(connection55),
  C56BP = mean(connection56),
  C57BP = mean(connection57),
  C58BP = mean(connection58),
  C59BP = mean(connection59),
  C60BP = mean(connection60),
  C61BP = mean(connection61),
  C62BP = mean(connection62),
  C63BP = mean(connection63),
  C64BP = mean(connection64),
  C65BP = mean(connection65),
  C66BP = mean(connection66),
  C67BP = mean(connection67),
  C68BP = mean(connection68),
  C69BP = mean(connection69),
  C70BP = mean(connection70),
  C71BP = mean(connection71),
  C72BP = mean(connection72),
  C73BP = mean(connection73),
  C74BP = mean(connection74),
  C75BP = mean(connection75),
  C76BP = mean(connection76),
  C77BP = mean(connection77),
  C78BP = mean(connection78),
  C79BP = mean(connection79),
  C80BP = mean(connection80),
  C81BP = mean(connection81),
  C82BP = mean(connection82),
  C83BP = mean(connection83),
  C84BP = mean(connection84),
  C85BP = mean(connection85),
  C86BP = mean(connection86),
  C87BP = mean(connection87),
  C88BP = mean(connection88),
  C89BP = mean(connection89),
  C90BP = mean(connection90),
  C91BP = mean(connection91),
  C92BP = mean(connection92),
  C93BP = mean(connection93),
  C94BP = mean(connection94),
  C95BP = mean(connection95),
  C96BP = mean(connection96),
  C97BP = mean(connection97),
  C98BP = mean(connection98),
  C99BP = mean(connection99),
  C100BP = mean(connection100),
  C101BP = mean(connection101),
  C102BP = mean(connection102),
  C103BP = mean(connection103),
  C104BP = mean(connection104),
  C105BP = mean(connection105)

  
  ) %>% 
  inner_join(data, by = "subject")  %>%
  mutate(C1WP=connection1 -C1BP,
         C2WP=connection2 -C2BP,
         C3WP=connection3 -C3BP,
         C4WP=connection4 -C4BP,
         C5WP=connection5 -C5BP,
         C6WP=connection6 -C6BP,
         C7WP=connection7 -C7BP,
         C8WP=connection8 -C8BP,
         C9WP=connection9 -C9BP,
         C10WP=connection10-C10BP,
         C11WP=connection11-C11BP,
         C12WP=connection12-C12BP,
         C13WP=connection13-C13BP,
         C14WP=connection14-C14BP,
         C15WP=connection15-C15BP,
         C16WP=connection16-C16BP,
         C17WP=connection17-C17BP,
         C18WP=connection18-C18BP,
         C19WP=connection19-C19BP,
         C20WP=connection20-C20BP,
         C21WP=connection21-C21BP,
         C22WP=connection22-C22BP,
         C23WP=connection23-C23BP,
         C24WP=connection24-C24BP,
         C25WP=connection25-C25BP,
         C26WP=connection26-C26BP,
         C27WP=connection27-C27BP,
         C28WP=connection28-C28BP,
         C29WP=connection29-C29BP,
         C30WP=connection30-C30BP,
         C31WP=connection31 -C31BP,
         C32WP=connection32 -C32BP,
         C33WP=connection33 -C33BP,
         C34WP=connection34 -C34BP,
         C35WP=connection35 -C35BP,         
         C36WP=connection36 -C36BP,      
         C37WP=connection37 -C37BP,         
         C38WP=connection38 -C38BP,         
         C39WP=connection39 -C39BP,         
         C40WP=connection40 -C40BP,         
         C41WP=connection41 -C41BP,
         C42WP=connection42 -C42BP,
         C43WP=connection43 -C43BP,
         C44WP=connection44 -C44BP,
         C45WP=connection45 -C45BP,
         C46WP=connection46 -C46BP,
         C47WP=connection47 -C47BP,
         C48WP=connection48 -C48BP,
         C49WP=connection49 -C49BP,
         C50WP=connection50 -C50BP,
         C51WP=connection51 -C51BP,
         C52WP=connection52 -C52BP,
         C53WP=connection53 -C53BP,
         C54WP=connection54 -C54BP,
         C55WP=connection55 -C55BP,
         C56WP=connection56 -C56BP,
         C57WP=connection57 -C57BP,
         C58WP=connection58 -C58BP,
         C59WP=connection59 -C59BP,
         C60WP=connection60 -C60BP,
         C61WP=connection61 -C61BP,
         C62WP=connection62 -C62BP,
         C63WP=connection63 -C63BP,
         C64WP=connection64 -C64BP,
         C65WP=connection65 -C65BP,
         C66WP=connection66 -C66BP,
         C67WP=connection67 -C67BP,
         C68WP=connection68 -C68BP,
         C69WP=connection69 -C69BP,
         C70WP=connection70 -C70BP,
         C71WP=connection71 -C71BP,
         C72WP=connection72 -C72BP,
         C73WP=connection73 -C73BP,
         C74WP=connection74 -C74BP,
         C75WP=connection75 -C75BP,
         C76WP=connection76 -C76BP,
         C77WP=connection77 -C77BP,
         C78WP=connection78 -C78BP,
         C79WP=connection79 -C79BP,
         C80WP=connection80 -C80BP,
         C81WP=connection81 -C81BP,
         C82WP=connection82 -C82BP,
         C83WP=connection83 -C83BP,
         C84WP=connection84 -C84BP,
         C85WP=connection85 -C85BP,
         C86WP=connection86 -C86BP,
         C87WP=connection87 -C87BP,
         C88WP=connection88 -C88BP,
         C89WP=connection89 -C89BP,
         C90WP=connection90 -C90BP,
         C91WP=connection91 -C91BP,
         C92WP=connection92 -C92BP,
         C93WP=connection93 -C93BP,
         C94WP=connection94 -C94BP,
         C95WP=connection95 -C95BP,
         C96WP=connection96 -C96BP,
         C97WP=connection97 -C97BP,
         C98WP=connection98 -C98BP,
         C99WP=connection99 -C99BP,
         C100WP=connection100 -C100BP,
         C101WP=connection101 -C101BP,
         C102WP=connection102 -C102BP,
         C103WP=connection103 -C103BP,
         C104WP=connection104 -C104BP,
         C105WP=connection105 -C105BP
  )

```

# Linear Models

## A note on the massive univariate models

PANAS_PA = fixed intercept (group level mean of PA) + C1WP (effect of connection1 within person) + C1BP (effect of connection1 between person) + daysFromFirstScan_STD (linear effect of time) + 1|subject (random intercept or deviation of the person level mean with respect to the group level mean PA).

PANAS_NA = fixed intercept (group level mean of NA) + C1WP (effect of connection1 within person) + C1BP (effect of connection1 between person) + daysFromFirstScan_STD (linear effect of time) + 1|subject (random intercept or deviation of the person level mean with respect to the group level mean NA).


Alors:\
intercept = group level mean of the dependent variable\
daysFromFirstScan_STD = linear effect of time\
C_X_WP= effect of connection "_X_" within person\
C_X_BP= effect of connection "_X_" between person



## Model for positive affectivity with BP effects
```{r, results = FALSE, message = FALSE}
results_PA=c()
for (i in 1:105) {
  vars = paste("C",i,"WP + C",i,"BP",sep= "")
  otherVars <- c("daysFromFirstScan_STD","(1|subject)")
  formList=lapply(vars,function(x) {reformulate(c(otherVars,x),response="PANAS_PA")})
  print(formList)
  res=summary(lapply(formList,lmer,data=dataML)[[1]])$coefficients
  results_PA=rbind(res,results_PA)
}
results_PA=as.data.frame(results_PA)
results_PA$sig=results_PA$`Pr(>|t|)`<0.05
```


FDR correction BP


```{r}
clean_results_PA = results_PA %>%
  filter(str_detect(row.names(results_PA), 'BP'))%>%
  mutate(pval.adj = p.adjust (`Pr(>|t|)`,"fdr"))%>%
  mutate(conn_names, .before=1)%>%as.data.frame()

clean_results_PA%>% kbl(booktabs = T, linesep = "") %>% 
  kable_paper(full_width = F) %>%column_spec(1:9, color = "white", background = case_when(clean_results_PA$pval.adj<0.10~"green",
                                                                                          clean_results_PA$'Pr(>|t|)'<0.05~"gold",
                                                                                          TRUE~"lightgray"))
```

FDR correction WP

```{r}
clean_results_PA = results_PA %>%
  filter(str_detect(row.names(results_PA), 'WP'))%>%
  mutate(pval.adj = p.adjust (`Pr(>|t|)`,"fdr"))%>%
  mutate(conn_names, .before=1)%>%as.data.frame()

clean_results_PA%>% kbl(booktabs = T, linesep = "") %>% 
  kable_paper(full_width = F) %>%column_spec(1:9, color = "white", background = case_when(clean_results_PA$pval.adj<0.10~"green",
                                                                                          clean_results_PA$'Pr(>|t|)'<0.05~"gold",
                                                                                          TRUE~"lightgray"))
```

## Model for negative affectivity with BP effects


```{r, results = FALSE, message = FALSE}
results_NA=c()
for (i in 1:105) {
  vars = paste("C",i,"WP + C",i,"BP",sep= "")
  otherVars <- c("daysFromFirstScan_STD","(1|subject)")
  formList=lapply(vars,function(x) {reformulate(c(otherVars,x),response="PANAS_NA")})
  print(formList)
  res=summary(lapply(formList,lmer,data=dataML)[[1]])$coefficients
  results_NA=rbind(res,results_NA)
}
results_NA=as.data.frame(results_NA)
results_NA$sig=results_NA$`Pr(>|t|)`<0.05
```

FDR correction BP

```{r}
clean_results_NA = results_NA %>%
  filter(str_detect(row.names(results_NA), 'BP'))%>%
  mutate(pval.adj = p.adjust (`Pr(>|t|)`,"fdr"))%>%
  mutate(conn_names, .before=1)%>%as.data.frame()

clean_results_NA%>% kbl(booktabs = T, linesep = "") %>% 
  kable_paper(full_width = F) %>%column_spec(1:9, color = "white", background = case_when(clean_results_NA$pval.adj<0.10~"green",
                                                                                          clean_results_NA$'Pr(>|t|)'<0.05~"gold",
                                                                                          TRUE~"lightgray"))
                                               
                                               


```


FDR correction WP

```{r}

clean_results_NA = results_NA %>%
  filter(str_detect(row.names(results_NA), 'WP'))%>%
  mutate(pval.adj = p.adjust (`Pr(>|t|)`,"fdr"))%>%
  mutate(conn_names, .before=1)%>%as.data.frame()

  
clean_results_NA%>% kbl(booktabs = T, linesep = "") %>% 
  kable_paper(full_width = F) %>%column_spec(1:9, color = "white", background = case_when(clean_results_NA$pval.adj<0.10~"green",
                                                                                          clean_results_NA$'Pr(>|t|)'<0.05~"gold",
                                                                                          TRUE~"lightgray"))
```

